Baseline centering problem

### 2019-01-10 paper/tangotd.tex

Another initialization might be $Z(s_1,s_2)\approx \frac{1}{1-\gamma}$
for every pair $s_1,s_2$. Indeed, on-policy, $Z$ is the density with
respect to the invariant distribution $\mu$, and for $\gamma$ close to
$1$, $Z$ will be approximately $\frac{1}{1-\gamma}$ plus a smaller function (see
below). Note that $Z(s_1,s_2)=\frac{1}{1-\gamma}$ is an exact solution of
the middle Bellman equation (as is $Z=0$), but it is a repulsive fixed
point, I think, so initializing to $\frac{1}{1-\gamma}$ plus noise should
converge to the true solution. Initializing there should have the
advantage of starting close to reasonable values.

@@

>>>>

Another initialization might be $Z(s_1,s_2)\approx \frac{1}{1-\gamma}$
for every pair $s_1,s_2$. Indeed, on-policy, $Z$ is the density with
respect to the invariant distribution $\mu$, and for $\gamma$ close to
$1$, $Z$ will be approximately $\frac{1}{1-\gamma}$ plus a smaller function (see
below). Note that $Z(s_1,s_2)=\frac{1}{1-\gamma}$ is an exact solution of
the middle Bellman equation (as is $Z=0$), but it is a repulsive fixed
point, I think, so initializing to $\frac{1}{1-\gamma}$ plus noise should
converge to the true solution [empirically I find this diverges]. Initializing there should have the
advantage of starting close to reasonable values.

@@

Normalization of $Z$. Since $Z=\sum \gamma^t P^t$, we have that
$(1-\gamma)Z$ is a stochastic matrix (thanks Yann). This might help with
normalization/detecting divergence. This translates as $\E_{s_2\sim \rho}
Z(s_1,s_2)=\frac{1}{1-\gamma}$ which is testable/enforceable. However, I
fear it might make the fixed point $Z(s_1,s_2)=\frac{1}{1-\gamma}$
attractive instead of repulsive, and it might also perturb initialization
(initializing $Z=\Id$ does not satisfy this normalization, so enforcing
it too early is basically like initializing to
$Z=\frac{1}{1-\gamma}\Id$ which empirically diverges).
